\thesistitle

### 2019-11-22 pldi/paper.tex
LLOC stuff

%% Title information
\title%[Short Title]
{A Code Clone Detection DSL for Java}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

\section{Clone Detection Techniques Survey}
As an initial step towards creating a clone detection DSL, we survey clone detection techniques and tools to extract common functionalities. \todo{Write this section}

@@

\subsection{Match Granularity}

>>>>

%% Title information
\title%[Short Title]
{CDD: A Code Clone Detection DSL for Java}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%\section{Clone Detection Techniques Survey} TODO
%As an initial step towards creating a clone detection DSL, we survey clone detection techniques and tools to extract common functionalities. \todo{Write this section}

@@

\subsection{Match Granularity}
The \textbf{Match} keyword describes on what granularity clones will be matched. CDD can find clones that span physical lines of code, logical lines of code and in subtrees of the AST of a program.% certain physical CDD supports three granularities:
\begin{itemize}
  \item \textbf{PLOC}: These are physical lines of code, excluding whitespace and comments. Comparison is done between the tokens found on the lines. The smallest clone that can be found using this approach is a single line clone.
  \item \textbf{LLOC}: These are logical lines of code, where each statement and some declarations are counted as a logical line of code \cite{nguyen2007sloc}. We compare these logical lines of code to find duplicates. The smallest clone that can be found using this approach is are clones that span a single logical line.
  \item \textbf{Subtree}: This method compares subtrees in the AST of the program.
\end{itemize}
